pema application

### 2023-02-01 paper/manuscript.Rmd
incorporate changes for publication

documentclass     : "apa6"
classoption       : "man"
knit: worcs::cite_essential
output            : papaja::apa6_pdf
header-includes:
  - \raggedbottom
---

```{r setup, include = FALSE}
run_everything <- FALSE
library("papaja")
library(tidySEM)
library(kableExtra)
r_refs("r-references.bib")
out <- readRDS("output.RData")
```

@@

We performed a simulation study to validate the BRMA algorithm.
As a benchmark for comparison, we used random effects meta-regression with restricted maximum likelihood estimation [RMA, @viechtbauerConductingMetaanalysesMetafor2010],
which is the current state-of-the-art in the field.
We evaluated the algorithms' predictive performance in new data, 
ability to perform variable selection,
and ability to recover population parameters.
Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
and which prior (LASSO versus regularized horseshoe) is to be preferred.
<span id = "defaultvalues">For both Bayesian priors, we used default values proposed in prior literature, see Table \@ref(tab:tabprior).
Default values for the LASSO prior were based on @ParkCasella2008,
and default values for the regularized horseshoe prior were based on @PiironenVehtari2017a.</span>
All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>.

@@

>>>>

documentclass     : "apa6"
classoption       : "man"
csl               : american-medical-association.csl
knit: worcs::cite_essential
output            : papaja::apa6_pdf
header-includes:
  - \raggedbottom
---

```{r setup, include = FALSE}
# Change the variable `run_everything` to TRUE to reproduce all analyses,
# including computer-intensive ones
run_everything <- FALSE
library("papaja")
library(tidySEM)
library(kableExtra)
r_refs("r-references.bib")
out <- readRDS("output.RData")
```

@@

We performed a simulation study to validate the BRMA algorithm.
As a benchmark for comparison, we used random effects meta-regression with restricted maximum likelihood estimation [RMA, @viechtbauerConductingMetaanalysesMetafor2010],
which is the current state-of-the-art in the field.
We evaluated the algorithms' predictive performance in new data, 
ability to perform variable selection,
and ability to recover population parameters.
Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
and which prior (LASSO versus regularized horseshoe) is to be preferred.
<span id = "defaultvalues">For both Bayesian priors, we used default values proposed in prior literature, see Table \@ref(tab:tabprior).
Default values for the LASSO prior were based on @ParkCasella2008,
and default values for the regularized horseshoe prior were based on @PiironenVehtari2017a.</span>
The simulation code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>, in the directory `pema/simulatie_2021`.

@@

# Data Availability Statement

All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>.
The directory `paper` contains the source code of this manuscript, 
and the directory `simulatie_2021` contains the simulation source code.
